%-------------------------------------------------------------------------
%   WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------

\section{experience}

\begin{entrylist}

%------------------------------------------------

\entry
{MVP}
{\href{}{Web SMS client}}
{React, Node/Express, MongoDB}
{\begin{itemize}
\item Implemented a client to send and receive text messages to mobile phones through Twilio API
\item Constructed a Django web application with interactive D3.js visualizations to showcase my data-driven ranking of scientific research: \href{http://forecite.us}{http://forecite.us}
\item Utilized MongoDB to persist messages between sessions.
\item TODO
\end{itemize}}

%------------------------------------------------

\entry
{Greenfield}
{\href{}{Rentlur}}
{Apr. 2016--Sep. 2016}
{\begin{itemize}
\item Implemented scraper and rendered dynamic listings page for all rental properties in a given craigslist locale.
\item Created details pages (along with image carousel) for each listing.
\end{itemize}}

%------------------------------------------------

\entry
{Legacy}
{\href{https://narrativescience.com/}{Reci-Calc}}
{React, Node/Express, PostgreSQL}
{\begin{itemize}
\item Refactored legacy codebase to decouple recipe creation to an intuitive design that requires lots of React properties rerouting.
\item  Deployed website on AWS using EC2 instance.
\item  Created a user friendly and intuitive saved recipe cards interface to persist between user sessions. 
\item Implemented a recipe suggestion based on a food search to help in creating recipes in a single interface. 
\end{itemize}}

%------------------------------------------------

\entry
{Thesis}
{\href{https://narrativescience.com/}{TBD}}
{React, Node/Express, TBD}
{\begin{itemize}
\item Refactored legacy codebase to decouple recipe creation to an intuitive design that requires lots of React properties rerouting.
\item  Deployed website on AWS using EC2 instance.
\item  Created a user friendly and intuitive saved recipe cards interface to persist between user sessions. 
\item Implemented a recipe suggestion based on a food search to help in creating recipes in a single interface. 
\item ONE MORE
\end{itemize}}

%------------------------------------------------
\end{entrylist}
